### 2013-04-25 inst/examples/allee.Rmd
tidying code

```{r libraries, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
require(tgp)
library(kernlab)
require(MCMCpack)
require(plyr)

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#sha <- gsub("^commit ", "", system("git log -n 1", intern=TRUE)[1])
#short_sha <- gsub("(^.{10}).*", "\\1", sha)
#date <- format(Sys.time(), "%Y-%m-%d-%H-%M-%S")
#opts_chunk$set(fig.path = paste("figure/", date, "-", short_sha, "-", sep=""))

@@

```{r}
dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
sim_plots(dt, seed=seed_i)
profits_stats(dt)
```

>>>>

```{r libraries, include=FALSE}
require(pdgControl)
require(nonparametricbayes)
require(reshape2)
require(ggplot2)
require(data.table)
require(tgp)
library(kernlab)
require(MCMCpack)
require(plyr)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

@@

```{r}
dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit, OptTime=OptTime)
sim_plots(dt, seed=seed_i)
profits_stats(dt)
```

### 2013-04-25 inst/examples/sensitivity.Rmd
tidying code

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#sha <- gsub("^commit ", "", system("git log -n 1", intern=TRUE)[1])
#short_sha <- gsub("(^.{10}).*", "\\1", sha)
#date <- format(Sys.time(), "%Y-%m-%d-%H-%M-%S")
#opts_chunk$set(fig.path = paste("figure/", date, "-", short_sha, "-", sep=""))
```

>>>>

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```
